Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-29 writeup/gz_hubble_data.tex
Adding full address to all affiliations.

\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, USA}
\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, USA}
\altaffiltext{3}{School of Physics and Astronomy, University of Nottingham, UK}
\altaffiltext{4}{Oxford Astrophysics, University of Oxford, UK}
\altaffiltext{5}{Institute of Cosmology and Gravitation, University of Portsmouth, UK}
\altaffiltext{6}{SEPnet, South East Physics Network, UK}
\altaffiltext{7}{Center for Astrophysics and Space Sciences, UC San Diego, USA}
\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, USA}
\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Japan}
\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, USA}
\altaffiltext{11}{Department of Astronomy and Astrophysics, Pennsylvania State University, USA}
\altaffiltext{12}{Centre for Astrophysics, University of Hertfordshire, UK}
\altaffiltext{13}{European Southern Observatory, Santiago, Chile}
\altaffiltext{14}{Department of Astronomy, Yale University, USA}
\altaffiltext{15}{Adler Planetarium, USA}
\altaffiltext{16}{Institute for Astronomy, ETH Z\"urich, Switzerland}
\altaffiltext{17}{GitHub}

>>>>

\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA}
\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA}
\altaffiltext{3}{School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK}
\altaffiltext{4}{Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
\altaffiltext{5}{Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK}
\altaffiltext{6}{SEPnet, South East Physics Network, UK}
\altaffiltext{7}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA}
\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA}
\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan}
\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
\altaffiltext{11}{Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{12}{Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK}
\altaffiltext{13}{European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile}
\altaffiltext{14}{Department of Astronomy, Yale University, New Haven, CT 06520, USA}
\altaffiltext{15}{Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA}
\altaffiltext{16}{Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland}
\altaffiltext{17}{GitHub}
